---
title: "Sanitary Violations: Final Project"
author: "Steven Espinoza"
date: "11/27/2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(leaflet)
library(plotly)
library(lubridate)
library(stringr)
library(janitor)
library(RSocrata)
library(tidyverse)
```

```{r loading_data, include=FALSE}
# Loading in the data from the API
df <- read.socrata("https://data.cambridgema.gov/resource/3c3f-byi2.csv")

# Making new columns for 'lat' and 'lng' and the difference in days between corrected_date - cited_date
df <- df %>% 
  separate(address, into = c('point', 'lng', 'lat'), sep = ' ') %>% 
  select(-point) %>% 
  
  # New column for lats and longs
  mutate(lng = gsub('\\(', "", lng), lat = gsub('\\)', "", lat)) %>% 
  
  # New column for time difference
  mutate(corrected_time = seconds_to_period(corrected_date - cited_date)$day)
```

```{r cleaning_names, echo=FALSE}
# Cleaning the "establishment names" column

# First step: making everything uppercase for sake of consistency
df <- df %>% 
  mutate(establishment_name = toupper(establishment_name))

# Removing apostrophes
for(i in length(df$establishment_name)){
  df$establishment_name[i] = str_replace(df$establishment_name[i], "\'", '')
}

```


## Sanitary Violations in Cambridge

The city of Cambridge maintains an open data set on sanitary violations as cited by the city's sanitary inspector. The dataset includes all kinds of checks that the sanitary inspector makes at food establishments, from making sure that a workers' hair is restrained to the prevention of contamination from hands. 

In total there are `r length(unique(df$case_number))` distinct cases in the dataset. There are also a total of `r length(unique(df$establishment_name))` establishments in the city of Cambridge.


```{r echo=FALSE, include=FALSE}
# Define UI for application that draws price-to-income ratios over time by selecting regions
shinyApp(
  
  ui <- fluidPage(
  
  # Application title
  titlePanel("Sanitary Violations"),
  
  sidebarPanel(
    # Select region name here
    selectInput(inputId = "name",
                label = "Name of Establishment",
                choices = sort(unique(df$establishment_name))),
    selectInput(inputId = 'case',
                label = 'Case Number',
                choices = "")),
  
  # Show a plot of the generated graph
  mainPanel(
    plotlyOutput("trendPlot")
  )),
  
# Define server logic required to draw a trend plot
server <- function(input, output, session){
  observe({
    x <- df %>% 
      filter(establishment_name == input$name) %>% 
      select(case_number) %>% 
      unique()
    
    updateSelectInput(session, "case",
                      label = 'Case Number',
                      choices = x)
  })
  
  
},
options = list(height=500)
)
```






